Low field depolarization of electronic spins through dipole-dipole coupling

### 2022-05-27 Mes papiers/Low field CR/SI/Low_field_CR_SI.tex
toto

Assuming a homogeneous distribution of the fluctuators in the bulk of the crystal, the authors conclude that the fluctuators create an additionnal decay channel for the NV population, through dipole-dipole interaction, characterized by a decay rate $\gamma$ which follows the probability distribution :
\begin{equation}
\rho(\gamma)=\frac{e^{-1/(4\gamma T)}}{\sqrt{4\pi \gamma^3 T}}
\end{equation}
Where the timescale $T$ is defined as
\begin{equation}
\frac{1}{T}=\left(\frac{4\pi n_fJ_0\bar \eta}{3}\right)^2 \frac{\pi}{\gamma_f}
\end{equation}
Where $n_f$ is the fluctuator density in the crystal in nm$^{-3}$, $J_0=52\ \rm{MHz}\cdot\rm{nm}^3$ is the characteristic dipole-dipole strength between two spins, $\gamma_f$ is the fluctuator intrinsic decay rate and $\bar \eta$ is a dimension-less number which characterizes the average dipole-dipole interaction between the NV centers and the fluctuators (resonance conditions, relative orientations etc. Further details are given below).

>>>>

Assuming a homogeneous distribution of the fluctuators in the bulk of the crystal, the authors of \cite{choi_depolarization_2017} conclude that the fluctuators create an additionnal decay channel for the NV population, through dipole-dipole interaction, characterized by a decay rate $\gamma$ which follows the probability distribution :
\begin{equation}
\rho(\gamma)=\frac{e^{-1/(4\gamma T)}}{\sqrt{4\pi \gamma^3 T}}
\end{equation}
Where the timescale $T$ is defined as
\begin{equation}
\frac{1}{T}=\left(\frac{4\pi n_fJ_0\bar \eta}{3}\right)^2 \frac{\pi}{\gamma_f}
\end{equation}
Where $n_f$ is the fluctuator density in the crystal in nm$^{-3}$, $J_0=52\ \rm{MHz}\cdot\rm{nm}^3$ is the characteristic dipole-dipole strength between two spins, $\gamma_f$ is the fluctuator intrinsic decay rate and $\bar \eta$ is a dimension-less number which characterizes the average dipole-dipole interaction between the NV centers and the fluctuators (resonance conditions, relative orientations etc. Further details are given below).
